### 2017-04-08 Manuscripts/cog-psych/cogpsych.tex
changed e2 colormap
added range diff figure to manuscript

To evaluate the role of contrast in category generation, we computed the number of times each stimulus was generated, as a function of its average city-block distance from members of the experimenter-defined ``Alpha'' category. These data, shown in Figure \ref{fig:e1-distanceplots}, reveal a clear pattern: examples that are more distant from members of the experimenter-defined categories are more likely to be generated into a new category.

@@

\begin{figure}
    \begin{center}
    \inputpgf{figs/}{e2-distanceplots.pgf}
    \caption{Experiment 2 results. \textit{Left}: Frequency of generation as a function of distance from members of the experimenter-defined category. \textit{Right}: Scatter plot of within-class versus between-class distance in each of the participant-generated categories.}
    \nbcnote{May want to change condition colors if purple-orange is used as the colormap for the range heat-maps in the simulations section.}
    \jlanote{sounds good to me.}
    \label{fig:e2-distanceplots}
    \end{center}
\end{figure}

@@

>>>>

To evaluate the role of contrast, we computed the number of times each stimulus was generated, as a function of its average city-block distance from members of the experimenter-defined ``Alpha'' category. These data, shown in Figure \ref{fig:e1-distanceplots}, reveal a clear pattern: examples that are more distant from members of the experimenter-defined categories are more likely to be generated into a new category.

@@

\begin{figure}
    \begin{center}
    \inputpgf{figs/}{e2-distanceplots.pgf}
    \caption{Experiment 2 results. \textit{Left}: Frequency of generation as a function of distance from members of the experimenter-defined category. \textit{Right}: Scatter plot of within-class versus between-class distance in each of the participant-generated categories.}
    \label{fig:e2-distanceplots}
    \end{center}
\end{figure}

@@

\begin{figure}[p]
    \begin{center}
    \inputpgf{figs/}{range-diff-gradients.pgf}
    \caption{Behavioral and simulated relative range gradients. Each panel shows, for each stimulus, the dimensional orientation of the categories it was generated into: vertically aligned `columns' versus horizontally aligned `rows'.}
    \label{fig:range-diff-gradients}
    \end{center}
\end{figure}
